Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-23 paper.tex
last fix

A set of 199 simulations was performed in which all five parameters in Table
\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of
those parameters, a set of 199 simulations was performed with only that
parameter being randomly varied, using the \gls{OFAT} method to estimated each
parameter contribution to the overall uncertianty.  A reference simulation was
performed with all five parameters fixed at the mean value.

@@

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined
once per deployed facility, each reactor will have a different cycle length
value, so a different number of batches loaded per year.  With the increase of
deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
the mean (reference) value, reducing its impact on the uncertainty on the total
uranium consumption. This uncertainty contribution to the overall uncertainty
decrease is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

@@

The uncertainty contribution from the cycle length between year 40 and 70 comes
mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution, the variation of cycle length being driving a
direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
Fuel enrichment and separation efficiency showed a relative contribution smaller
than $0.4\%$.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Nevertheless such conclusions might constrained by the simulation
different hypothesis: not considering radioactive decay removes the decay of
$^{241}$Pu during cooling and considering a transition to fast reactors
minimizes the impact of the discharge composition change induced by the cycle
length variations.

>>>>

A set of 199 simulations was performed in which all five parameters in Table
\ref{tab:package_uncertainty} are randomly varied. Additionally, for each of
those parameters, a set of 199 simulations was performed with only that
parameter being randomly varied, using the \gls{OFAT} method to estimated each
parameter contribution to the overall uncertainty.  A reference simulation was
performed with all five parameters fixed at the mean value.

@@

The decrease of the cycle time uncertainty contribution, from year 30 to year
90, can be understood as an averaging effect.  As the uncertainty are defined
once per deployed facility, each reactor will have a different cycle length
value, so a different number of batches loaded per year.  With the increase of
deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
the mean (reference) value, reducing its impact on the uncertainty on the
uranium consumption. This uncertainty contribution to the overall uncertainty
decrease is proportional to the number of \gls{LWR} reactors and stops with the
decommission of the last one.

@@

The uncertainty contribution from the cycle length between year 40 and 70 comes
mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
years this contribution follows the thermal power contribution closely,
suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
mechanism of this contribution, the variation of cycle length being driving a
direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
Both the fuel enrichment and separation efficiency showed a relative
contribution smaller than $0.4\%$.

@@

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Nevertheless such conclusions are constrained by the simulation
hypothesis: not considering radioactive decay removes the decay of $^{241}$Pu
during cooling and considering a transition to fast reactors minimizes the
impact of the discharge composition change induced by the cycle length
variations, when reprocessing them to build the next \gls{MOX} fuel batch.
